Rule Synthesis for Rule-based Intrusion Detectors

### 2020-05-26 paper/paper.tex
pass

    \midrule
    Black Nurse & 1 & 4 & 9 & 2 \\    
    Ping Scan & 6 & 5 & 9 & 2 \\
    SYN Flood & 4 & 2 & 2 & 1 \\
    UDP Teardrop & 1 & 4 & 8 & 4 \\
    2100384 & 13 & 8 & 18 & 2 \\
    2100399 & 132 & 6 & 3 & 1 \\
    2100401 & 12 & 6 & 25 & 1 \\
    2100402 & 3 & 6 & 12 & 1 \\
    2100408 & 15 & 8 & 9 & 2 \\
    2100485 & 4 & 6 & 3 & 1 \\
    2100486 & 195 & 6 & 2 & 1 \\
    %%UDP Flood & - & - & - & - \\
    \midrule
    %%Apache Struts 2 & 2 & 65 & - & - \\
    ColdFusion & 7 & 19 & 40 & 4\\
    iisadmin access & 3 & 17 & 605 & 1 \\        
    JBoss JMX & 5 & 23 & 925 & 87 \\
    scripttag & 23 & 22 & 2,221 & 1 \\
    WeBid LFI & 1 & 23 & 35,444 & 17\\    
    %%Wordpress Login & 8 & 59 & - & - \\
    .htaccess access & 5 & 17 & 852 & 1\\
    .idq access & 14 & 19 & 806 & 2 \\
    /system32/ in URI & 4 & 20 & 1881 & 2 \\
    Basebuilder LFI & 1 & 22 & 60222 & 48 \\
    Tomcat Snoop Access & 1 & 24 & 58,122 & 37 \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

    \midrule
    Black Nurse & 1 & 4 & 9 & 2 \\    
    Ping Scan & 6 & 5 & 9 & 2 \\
    SYN Flood & 4 & 2 & 2 & 1 \\
    UDP Teardrop & 1 & 4 & 8 & 4 \\
    2100384 & 13 & 8 & 18 & 2 \\
    2100399 & 132 & 6 & 3 & 1 \\
    2100401 & 12 & 6 & 25 & 1 \\
    2100402 & 3 & 6 & 12 & 1 \\
    2100408 & 15 & 8 & 9 & 2 \\
    2100485 & 4 & 6 & 3 & 1 \\
    2100486 & 195 & 6 & 2 & 1 \\
    %%UDP Flood & - & - & - & - \\
    \midrule
    %%Apache Struts 2 & 2 & 65 & - & - \\
    ColdFusion & 7 & 19 & 40 & 4\\
    iisadmin access & 3 & 17 & 605 & 1 \\        
    JBoss JMX & 5 & 23 & 925 & 87 \\
    scripttag & 23 & 22 & 2,221 & 1 \\
    WeBid LFI & 1 & 23 & 35,444 & 17\\    
    %%Wordpress Login & 8 & 59 & - & - \\
    .htaccess access & 5 & 17 & 852 & 1\\
    .idq access & 14 & 19 & 806 & 2 \\
    /system32/ in URI & 4 & 20 & 1,881 & 2 \\
    Basebuilder LFI & 1 & 22 & 60,222 & 48 \\
    Tomcat Snoop Access & 1 & 24 & 58,122 & 37 \\
    \bottomrule
  \end{tabular}
\end{table}
